---
output: github_document
---

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prettynumbers

The goal of prettynumbers is to provide a pretty print method for (large)
numbers, primarily for the type vector . Before a more extended autoprint is
implemented in base R, we need to call `print` explicitly, but hopefully this
will be [resolved until R
3.6](https://twitter.com/_lionelhenry/status/1014078544086003712).

## Installation

You can install the development version from GitHub.

```{r, eval = FALSE}
devtools::install_github("lorenzwalthert/prettynumbers") 
```

## Example


```{r example}
set.seed(4)
library(prettynumbers)
numbers <- c(1, 23, 1023.30, 38929381, runif(10, 0, 1e6))
numbers
```

Note that because of autoprint for interactive usage is not implemented as 
stated above, you need to call `print()` explicitly when used interactively, 
e.g.

```{r}
print(numbers, delim = ",", digits_after_decimal = 2)
```

And see how this compares to the default printing method:
```{r}
set.seed(4)
c(1, 23, 1023.30, 38929381, runif(10, 0, 1e6)) %>% print.default()
```


## Features

Compared the default interger and numberic printing method, this package offers. 

* Allign numbers by decimal point.
* Print only one number per row to reduce distortion.
* Add delimiters such as `'`. 
* Show rounded output in semi-verbatin for easier visual digestion.
* limit number of printed elements.

